### 2020-08-07 data/draft-sections.tex
clean generation
code for visitors, generating

@@

@@

\item {\bf SANCHAYAN SEN\,:} Sole investigator in a Science & Engineering Research Board (SERB) project
\begin{description}
  \item[Project Title\,:] Geometry of random discrete structures
  \item[Duration\,:] 2020--2023
  \item[Grant\,:] 220,000 per annum
\end{description}

@@

@@

\subsection{Other Activities: 2019-20}
\begin{enumerate}
\item A. K. Nandakumaran was Convener, KVPY
\item A. K. Nandakumaran was Member, Library Committee
\item Apoorva Khare was Member of two UG Project Presentation Evaluation Committees
\item Apoorva Khare was Pre-RMO (Regional Mathematics Olympiad) - helped in setting the question paper
\item Apoorva Khare was Senate nominee for Comprehensive Exam of Vinayak Ramkumar (student of P. Vijay Kumar, ECE)
\item Apoorva Khare was Advising: (1) Prateek Kumar Vishwakarma, Int-PhD (passed his Comprehensive Exam) (2) Babhrubahan Bose, Int-PhD (passed his Comprehensive Exam) (3) G.V.K. Teja, PhD (passed his Comprehensive Exam) (4) Swarnalipa Datta, Int-PhD (downgraded to MS) Mentoring: (5) Dr. Projesh Nath Choudhury, NBHM postdoc
\item Arvind Ayyer was Referee for the thesis of Majil Pratim Saikia at University of Vienna.
\item Arvind Ayyer was Referee for the thesis of Mr. Jyotirmoy Ganguly at IISER Pune.
\item Arvind Ayyer was Thesis examiner for Mr. Sudip Bera, Visva-Bharati University.
\item Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)
\item Gautam Bharali was Served as an independent expert for the Swiss National Science Foundation for the review of project proposals in pure mathematics in 2019.
\item R VENKATESH was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
\item R VENKATESH was Discussion Meeting on Representation Theory 2019, Department of Mathematics, IISc, Bangalore (December 14 - 16, 2019). Partially funded by the UGC-CAS grant.  Two lecture series was delivered by Professor Vyjayanthi Chari (UC Riverside, USA) and Professor Anne Schilling (UC Davis, USA) as part of this discussion meeting. 
\item R VENKATESH was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
\item Siddhartha Gadgil was thesis examiner for a thesis at IIT, Kanpur
\item Siddhartha Gadgil was thesis examiner for a thesis at Delhi University
\item Siddhartha Gadgil was thesis examiner for a thesis for TIFR, Mumbai
\item Siddhartha Gadgil was member of selection committee at BHU
\item Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune. 
\item Subhojoy Gupta was Co-organizer of an Advanced Instructional School on Riemannian Geometry, sponsored by the National Centre for Mathematics, held in July 2019.
\item Subhojoy Gupta was Referee for "Proceedings of the London Mathematical Society", "Journal of Topology", "Manuscripta Mathematica" and reviewer for AMS and Zentralblatt Math Reviews
\item Subhojoy Gupta was Supervised UG final year project of Shabarish Chenakkod
\end{enumerate}

>>>>

\item {\bf Abhishek Banerjee\,:} Sole investigator in a SERB project
\begin{description}
  \item[Project Title\,:] MATRICS Grant : MTR/2017/000112("Algebraic Geometry over symmetric monoidal categories and tensor triangular geometry")
  \item[Duration\,:] 2018-2021
  \item[Grant\,:] Rs 6.6 lakh
\end{description}

@@

\item {\bf Gadadhar Misra\,:} Sole investigator in a SERB project
\begin{description}
  \item[Project Title\,:] The role of curvature in Operator Theory
  \item[Duration\,:] 2018 - 2021
  \item[Grant\,:] 660000
\end{description}

\item {\bf Gadadhar Misra\,:} Sole investigator in a SERB project
\begin{description}
  \item[Project Title\,:] J C Bose Fellowship
  \item[Duration\,:] 2018 - 2021
  \item[Grant\,:] 
\end{description}

@@

\item {\bf SANCHAYAN SEN\,:} Sole investigator in a Science \& Engineering Research Board (SERB) project
\begin{description}
  \item[Project Title\,:] Geometry of random discrete structures
  \item[Duration\,:] 2020--2023
  \item[Grant\,:] 220,000 per annum
\end{description}

@@

\item Gadadhar Misra was Convener, Symposium: Mathematics and Society, INSA Anniversary Conference, Dec 2019

@@

\subsection{Other Activities: 2019-20}
\begin{enumerate}
\item A. K. Nandakumaran was Convener, KVPY
\item A. K. Nandakumaran was Member, Library Committee
\item Apoorva Khare was Member of two UG Project Presentation Evaluation Committees
\item Apoorva Khare was Pre-RMO (Regional Mathematics Olympiad) - helped in setting the question paper
\item Apoorva Khare was Senate nominee for Comprehensive Exam of Vinayak Ramkumar (student of P. Vijay Kumar, ECE)
\item Apoorva Khare was Advising: (1) Prateek Kumar Vishwakarma, Int-PhD (passed his Comprehensive Exam) (2) Babhrubahan Bose, Int-PhD (passed his Comprehensive Exam) (3) G.V.K. Teja, PhD (passed his Comprehensive Exam) (4) Swarnalipa Datta, Int-PhD (downgraded to MS) Mentoring: (5) Dr. Projesh Nath Choudhury, NBHM postdoc
\item Arvind Ayyer was Referee for the thesis of Majil Pratim Saikia at University of Vienna.
\item Arvind Ayyer was Referee for the thesis of Mr. Jyotirmoy Ganguly at IISER Pune.
\item Arvind Ayyer was Thesis examiner for Mr. Sudip Bera, Visva-Bharati University.
\item Gadadhar Misra was Member, Scientific Committee, Hilbert Modules in Analytic Function Spaces workshop,     Tsinghua Sanya International Mathematics Forum (TSIMF), Sanya, China, Dec 30, 2019 - Jan 3, 2020
\item Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)
\item Gautam Bharali was Served as an independent expert for the Swiss National Science Foundation for the review of project proposals in pure mathematics in 2019.
\item R VENKATESH was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
\item R VENKATESH was Discussion Meeting on Representation Theory 2019, Department of Mathematics, IISc, Bangalore (December 14 - 16, 2019). Partially funded by the UGC-CAS grant.  Two lecture series was delivered by Professor Vyjayanthi Chari (UC Riverside, USA) and Professor Anne Schilling (UC Davis, USA) as part of this discussion meeting.
\item R VENKATESH was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
\item Siddhartha Gadgil was thesis examiner for a thesis at IIT, Kanpur
\item Siddhartha Gadgil was thesis examiner for a thesis at Delhi University
\item Siddhartha Gadgil was thesis examiner for a thesis for TIFR, Mumbai
\item Siddhartha Gadgil was member of selection committee at BHU
\item Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune.
\item Subhojoy Gupta was Co-organizer of an Advanced Instructional School on Riemannian Geometry, sponsored by the National Centre for Mathematics, held in July 2019.
\item Subhojoy Gupta was Referee for "Proceedings of the London Mathematical Society", "Journal of Topology", "Manuscripta Mathematica" and reviewer for AMS and Zentralblatt Math Reviews
\item Subhojoy Gupta was Supervised UG final year project of Shabarish Chenakkod
\end{enumerate}

### 2020-08-07 data/reports.tex
code for visitors, generating

@@

@@

(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases G = E_6,7,8 and F_4 and thus completed the main theorems of the papers of V. Chari and et al., (J. Algebra, 2016) and Deniz Kus and et al., (Represent. Theory., 2016). Obtained a new combinatorial proof for the key fact that was used in  V. Chari and et al., (J. Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules. This key fact was proved only for the cases when G is the classical type and G_2 in their paper and they also proved it by analysing case-by-case. Our proof is uniform avoids the case-by-case analysis and works for all finite-dimensional simple Lie algebras.  (b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras. Simplifying the generators and relations of these modules is very crucial in their study. We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.   (c) A number of conjectures made about the graded characters affine Demazure modules of affine sl_3 using data obtained from SAGE.

@@

(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases G = E_6,7,8 and F_4 and thus completed the main theorem of the paper of V. Chari and et al., (J. Algebra, 2016). Obtained a new combinatorial proof for the key fact that was used in  V. Chari and et al., (J. Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules. This key fact was proved by V. Chari and et al., (J. Algebra, 2016) only for the cases when G is the classical types and G_2 and they did a case-by-case analysis to prove this. Our new proof is very uniform and avoids the case-by-case analysis and works in general.  (b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras. Simplifying the generators and relations of these modules is very crucial in their study. We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.   (c) A number of conjectures made about the graded characters affine Demazure modules of affine sl_3 using data obtained from SAGE.

@@

>>>>

\subsection{Abhishek Banerjee}

@@

\subsection{Gadadhar Misra}

There is a one to one correspondence between holomorphic imprimitivities and the holomomorphic hermitian homogeneous vector bundles on a bounded symmetric domain D. The homogeneous bundles can be obtained by holomorphic induction from representations of a certain parabolic Lie algebra on finite dimensional inner product spaces. The representations, and the induced bundles, have composition series with irreducible factors. In joint work with A. Koranyi, our first main result is the construction of an explicit differential operator intertwining the bundle with the direct sum of its factors. Next, we study Hilbert spaces of sections of these bundles. We use this to get, in particular, a full description and a similarity theorem for homogeneous n-tuples of operators in the Cowen-Douglas class of the Euclidean unit ball.   Beurling’s theorem shows that all submodules of the Hardy module are isomorphic leading to the question of rigidity of submodules in multi-variate operator theory. The submodules of analytic Hilbert modules defined over certain algebraic varieties in bounded symmetric domains, the so-called Jordan-Kepler varieties X of arbitrary rank r have been studied. For r > 1, the singular set of X is not a complete intersection. Hence the usual monoidal transformations do not suffice for the resolution of the singularities. Instead (joint with Upmeier), we describe a new higher rank version of the blow-up process, defined in terms of Jordan algebraic determinants, and apply this resolution to obtain the rigidity of the sub-modules vanishing on the singular set.   (with Koranyi) Homogeneous Hermitian holomorphic vector bundles and the Cowen-Douglas class over bounded symmetric domains, Adv. Math., 351 (2019), 1105 - 1138.  (with Upmeier)  Singular Hilbert modules on Jordan-Kepler varieties, To appear, Proceedings of IWOTA 2018, in memory of R. G. Douglas.

@@

(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases $G = E_6,7,8$ and $F_4$ and thus completed the main theorems of the papers of V. Chari and et al., (J. Algebra, 2016) and Deniz Kus and et al., (Represent. Theory., 2016). Obtained a new combinatorial proof for the key fact that was used in  V. Chari and et al., (J. Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules. This key fact was proved only for the cases when G is the classical type and $G_2$ in their paper and they also proved it by analysing case-by-case. Our proof is uniform avoids the case-by-case analysis and works for all finite-dimensional simple Lie algebras.  (b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras. Simplifying the generators and relations of these modules is very crucial in their study. We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.   (c) A number of conjectures made about the graded characters affine Demazure modules of affine $sl_3$ using data obtained from SAGE.

@@

(a) Settled the decomposition theorem for G-stable affine Demazure modules for the cases $G = E_6,7,8$ and $F_4$ and thus completed the main theorem of the paper of V. Chari and et al., (J. Algebra, 2016). Obtained a new combinatorial proof for the key fact that was used in  V. Chari and et al., (J. Algebra, 2016) to prove the decomposition of G-stable affine Demazure modules. This key fact was proved by V. Chari and et al., (J. Algebra, 2016) only for the cases when G is the classical types and $G_2$ and they did a case-by-case analysis to prove this. Our new proof is very uniform and avoids the case-by-case analysis and works in general.  (b) Simplified the presentation of all affine Demazure modules of untwisted affine Kac–Moody Lie algebras. Simplifying the generators and relations of these modules is very crucial in their study. We are investigating how to use this simplified presentation of affine Demazure modules to study Schur positivity type questions which arise naturally in Algebraic Combinatorics.   (c) A number of conjectures made about the graded characters affine Demazure modules of affine $sl_3$ using data obtained from SAGE.

@@

\subsection{Dr. Abhitosh Upadhyay}

\subsection{Anupam Gumber}

I have been working as a NBHM-postdoctoral fellow at IISc Bangalore under the mentorship of  Prof. S. Thangavelu since March 28, 2019. During the period between April 01, 2019-March 31, 2020 at IISc, along with some research discussions with Prof. S. Thangavelu, I was also involved in working on research problems jointly with Prof. P. K. Ratnakumar (HRI Prayagraj, India), Prof. Joachim Toft (Linnaeus Univ., Sweden) and Prof. Hans G. Feichtinger (NuHAG Group Leader, Univ. Vienna, Austria). The questions considered require the interplay between harmonic analysis, time-frequency analysis and approximation theory. The following is a brief detailed report of my research work during the above mentioned period at IISc:   \begin{itemize} \item [(I)] {\large{\bf Translation and modulation invariant Hilbert spaces:}} In a joint work with Prof. Joachim Toft and other collaborators, we have investigated the translation and modulation invariant Hilbert spaces. In this regard, we have shown that any Hilbert space of distributions on $\mathbb{R}^d$ which is translation and modulation invariant, also in the sense of its norm, is equal to $L^2(\mathbb{R}^d)$, with the same norm apart from a multiplicative constant. The manuscript has been communicated to a journal.   \item [(II)] {\large{\bf On Weyl multipliers and twisted modulation spaces:}} In a joint collaboration with Prof. P. K. Ratnakumar, we have studied the twisted modulation spaces and characterise the Weyl multipliers on them. The analysis also leads to the characterisation of multiplication operators on certain non-commutative amalgam spaces. The technical work relies on the harmonic analysis of special Hermite operator, also called the twisted Laplacian on $\mathbb{C}^n$. The manuscript is to be submitted soon.  \item [(III)] {\large{\bf{Completeness of shifted dilates in invariant Banach spaces of distributions:}}} Jointly with Prof. Hans G. Feichtinger,  we  show that the well established methods from the theory of Banach modules and time-frequency analysis allow to derive completeness results for the collection of shifted and dilated version of a given (test) function in a quite general setting. While the basic ideas show strong similarity to the arguments used in a recent paper by V. Katsnelson [1], we extend his results in several directions, both relaxing the assumptions (instead of a Gauss function any function with non-vanishing integral can be used), and widening the range of applications considerably. There is no need for the Banach spaces considered to be embedded into $(L^2(\mathbb{R}), ||\cdot{}||_2 )$, nor is the Hilbert space structure relevant. We choose to present the results in the setting of the Euclidean spaces, because then the  space of tempered distributions $S^{\prime}(\mathbb{R}^d) (d \geq 1)$  provides a well-established environment for mathematical analysis. In addition, we establish connections to modulation spaces, and specifically to the Shubin classes $(Q_s(\mathbb{R}^d), ||\cdot{}||_{Q_s})$, by showing that they are indeed special cases of Katsnelson's setting. The technical work for the results involved is almost done. The final writing of the manuscript is in progress. \end{itemize}  References: [1] V. Katsnelson, On the completeness of Gaussians in a Hilbert functional space, {\em Complex Anal. Oper. Theory}, 13(3) (2019) 637-658.
